\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}                
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{eurosym}

\firstname{Antoine}
\familyname{POUILLAUDE}
\title{Student in computer engineering at the UTC}              
\address{44 Square de la Mare-Gaudry}{60200 Compiègne (FRANCE)}    
\mobile{+33675468528}                    
\email{pouillaude.a@gmail.com}
\homepage{antony-po.net}
\extrainfo{Driving licence}
 
\begin{document}
\maketitle
Student in computer engineering, I want to work in Canada or in the United States of America after I graduate. Therefore I am glad to be able to do a 6-month exchange at the University of Rhodes Island.
\newline{}

\section{Educations}
\cventry{Feb. 2011\\to present}{Diplôme d'ingénieur en Informatique}{(5-year Engineering degree in computer science)}{}{}{Université de Technologie de Compiègne, Compiègne (FRANCE) \newline}
\cventry{Sep. 2010\\to Feb. 2011}{Classe Préparatoire}{(6 months of preparation program for competitive exams)}{}{}{Lycée Michel de Montaigne, Bordeaux (FRANCE) \newline}
\cventry{Jun. 2010}{Baccalauréat Scientifique}{(French secondary diploma, with emphasis in mathematics)}{}{}{Lycée Bernard Palissy, Saintes (FRANCE)}

\section{Experience}
\cventry{Jul. 2013\\to Aug. 2013}{Ramp agent}{Cassidian Aviation Training Services}{Cognac}{France}{In charge of helping pilots during departure and arrival procedures, filling the planes fuel tanks, handing out parachutes to pilots \newline{}}
\cventry{Apr. 2013\\to Jun. 2013}{Object-Oriented Programming Project}{Notes Manager}{UTC}{}{Designing and programming software with Qt/C++ to manage notes\newline{} https://github.com/AntoineC-12/Notify}
\cventry{}{Database designing and managing project}{}{UTC}{}{Designing of database based on specifications and development of a PHP interface to manage the it \newline{} https://github.com/AntoineC-12/NF17\_{}projet \newline{}}
\cventry{Jul. 2012\\to Aug. 2012}{Head of the ferryboat}{City Hall of Chaniers}{Chaniers}{France}{In charge of driving the ferry \newline{}}

\section{Skills}
\subsection{Computer}
\cvcomputer{Languages}{C, C++, Python, PHP, Go, Lisp}{Framework}{Qt, Angular.js, Bootsrtap}
\cvcomputer{Softwares}{XCode, Qt Creator, Microsoft Office Suite}{Others}{Operational on Mac OSX, Windows, Linux}

\subsection{Languages}
\cvlanguage{English}{Fluent}{104 points at the TOEFL test, C1}
\cvlanguage{Spanish}{Good level}{B2}
\cvlanguage{Chinese}{Notions}{A2}
\cvlanguage{French}{Mothertongue}{}

\newpage

\section{Miscellaneous}
\cvline{Sport}{12 years of practice of swimming.\newline{}
Tennis and badminton. \newline{}}
\cvline{Hobbies}{Pilot of single-engine planes (Robin DR400, Jodel D113V), Pilot’s license obtained in 2009 \newline{}
11 years of practicing piano \newline{}}
\cvline{Associations}{President of the association Poker\'{}UTC, Université de Technologie de Compiègne \newline{}
Treasurer of the association FabLab\'{}UTC, Université de Technologie de Compiègne \newline{}(assos.utc.fr/fablab)
\newline{}}
\cvline{Computer}{Creating my own Web server on a reused computer (problems with Bind9)\newline{}
Developing a bank accounts management software with C++/Qt}
\end{document}
